Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-10-08 paper/paper.tex
formatting changes requested by _eLife_

\begin{abstract}
The outcome of viral infection is extremely heterogeneous, with infected cells only sometimes activating innate immunity.  
Here we assess how the genetic variation inherent in viral populations contributes to this heterogeneity.
We do this by developing a new approach to determine both the transcriptome and full-length sequences of all viral genes in single influenza-infected cells.
Infections that activate an innate-immune response in single cells are associated with viral defects that include amino-acid mutations, internal deletions, and failure to express key genes.  
However, immune activation remains stochastic in cells infected by virions with these defects, and sometimes occurs even in cells infected by virions that express unmutated copies of all genes.
Our work shows that the genetic variation present in influenza virus populations substantially contributes to but does not fully explain the heterogeneity in infection outcome and immune activation in single infected cells.
\end{abstract}

@@

\section{Acknowledgments}
We thank Cole Trapnell, Jason Underwood, Robert Bradley, Daniel Stetson, AJ Velthuis, Katherine Xue, and Hannah Itell for helpful suggestions.
We thank Andy Marty and the Fred Hutch Genomics Core for performing the deep sequencing.
This work was supported by the NIAID of the NIH under grant R01 AI127893 and a Burroughs Wellcome Fund Young Investigator in the Pathogenesis of Infectious Diseases grant to JDB.
ABR was supported by a postdoctoral fellowship from the Damon Runyon Cancer Research Foundation.
JRK was supported by a Washington Research Foundation Undergraduate Research Fellowship and a Mary Gates undergraduate research scholarship from the University of Washington.
JDB is an Investigator of the Howard Hughes Medical Institute.
The funders had no role in study design, data collection and interpretation, or the decision to submit the work for publication.

>>>>

\begin{abstract}
The outcome of viral infection is extremely heterogeneous, with infected cells only sometimes activating innate immunity~\citep{russell2018extreme}.  
Here we assess how the genetic variation inherent in viral populations contributes to this heterogeneity.
We do this by developing a new approach to determine both the transcriptome and full-length sequences of all viral genes in single influenza-infected cells.
Infections that activate an innate-immune response in single cells are associated with viral defects that include amino-acid mutations, internal deletions, and failure to express key genes.  
However, immune activation remains stochastic in cells infected by virions with these defects, and sometimes occurs even in cells infected by virions that express unmutated copies of all genes.
Our work shows that the genetic variation present in influenza virus populations substantially contributes to but does not fully explain the heterogeneity in infection outcome and immune activation in single infected cells.
\end{abstract}

@@

\section{Acknowledgments}
We thank Cole Trapnell, Jason Underwood, Robert Bradley, Daniel Stetson, AJ Velthuis, Katherine Xue, and Hannah Itell for helpful suggestions.
We thank Andy Marty and the Fred Hutch Genomics Core for performing the deep sequencing.
%This work was supported by the NIAID of the NIH under grant R01 AI127893 and a Burroughs Wellcome Fund Young Investigator in the Pathogenesis of Infectious Diseases grant to JDB.
%ABR was supported by a postdoctoral fellowship from the Damon Runyon Cancer Research Foundation.
%JRK was supported by a Washington Research Foundation Undergraduate Research Fellowship and a Mary Gates undergraduate research scholarship from the University of Washington.
%JDB is an Investigator of the Howard Hughes Medical Institute.
%The funders had no role in study design, data collection and interpretation, or the decision to submit the work for publication.
